### 2020-06-13 system-model.tex
:pencil: SWIPT review

>>>>

\begin{section}{Introduction}
	With the significant advance in communication performance (throughput, latency, outage), the main challenge of wireless network has come to energy supply. Most existing mobile devices are powered by batteries that require frequent charging or replacement, which leads to high maintenance cost and restricts the scale of networks. Although solar energy and inductive coupling has become popular alternatives, the former depends on the environment while the latter has a very short operation range. Simultaneous Wireless Information and Power Transfer (SWIPT) is a promising solution to connect and power mobile devices via electromagnetic (EM) waves in the radio-frequency (RF) band. It provides low power (in \si{\uW} level) but broad coverage (up to hundreds of meters) \cite{Ng2018} in a sustainable and controllable manner. The trend of reduction in electronic power consumption also boosts the paradigm shift from dedicated power source to Wireless Power Transfer (WPT) and SWIPT.

	The concept of SWIPT were first cast in \cite{Varshney2008}, where the authors investigated the rate-energy (R-E) tradeoff for a flat Gaussian channel and some discrete channels. Two practical receiver structures were then proposed in \cite{Zhou2013}, namely Time Switching (TS) that switch between energy harvesting (EH) and Information Decoding (ID) modes and Power Splitting (PS) that splits the received signal into individual components. On top of this, \cite{Zhang2013} characterized the R-E region for a multiple-input multiple-output (MIMO) broadcast system under TS and PS setup. Information and power beamforming was then considered in multi-user multi-input single-output (MISO) systems to maximize the weighted sum-power subjective to SINR constraints \cite{Xu2014}. Motivated by this, \cite{Krikidis2014} investigated fundamental transceiver modules, information and power scheduling, and interference management for SWIPT systems. However, \cite{Boshkovska2015} pointed out that the Radio Frequency (RF)-to-Direct Current (DC) conversion efficiency depends on the harvester input power level. The authors also suggested a practical parametric harvester model based on curve fitting and proposed an iterative resource allocation algorithm. From another perspective, \cite{Trotter2009,Boaventura2011} demonstrated that multisine waveform outperforms single tone in both operation range and RF-to-DC efficiency, which is more suitable for WPT. In \cite{Clerckx2016a}, a tractable diode nonlinear model was derived based on the Taylor expansion of diode I-V characteristics and proposed an adaptive waveform optimization algorithm to maximize the output DC current. Simulation and experiments demonstrated the benefit of modelling rectifier nonlinearity in system design \cite{Kim2019,Kim2019a}. The work was extended to SWIPT in \cite{Clerckx2018} where a superposition of modulated information waveform and multisine power waveform is optimized to enlarge the R-E region. In contrast, \cite{Park2018} suggested an adaptive dual-mode SWIPT alternating between single-tone transmission that exploits conventional modulation for high-rate applications and multisine transmission that boosts the energy while encoding the information in the Peak-to-Average Ratio (PAPR) for power-demanding applications. Assuming On-Off-Keying (OOK) where bit 1 carries energy, \cite{Hu2019} compared unary and Run-Length-Limited (RLL) code in terms of rate vs battery overflow/underflow probability, and adjusted conventional modulation schemes such that WPT is only activated at the points with large offset. Also, a learning approach \cite{Varasteh2019c} demonstrated that the offset of the power symbol is positively correlated to the energy constraint, while the information symbols are symmetrically distributed around the origin. It confirmed that the superposed waveform is feasible to enlarge R-E region when considering rectifier nonlinearity. SWIPT was also applied in the network design of Non-Orthogonal Multiple Access (NOMA) and Rate-Splitting Multiple Access (RSMA). \cite{Liu2016} proposed a cooperative SWIPT NOMA protocol with three user selection schemes to enable the strong user assists the EH of the weak user. In \cite{Mao2019}, SWIPT was formulated as a Weighted-Sum Rate (WSR) maximization problem subject to total harvested energy constraint for separated Information Receivers (IRs) and Energy Receivers (ERs).

	Intelligent Reflecting Surface (IRS) adapts the wireless environment to increase spectrum and energy efficiency. A practical IRS consists of multiple individual elements that adjust the incident signal in terms of amplitude and phase through passive beamforming \cite{Wu2019e}. Different from relay and backscatter communication, it assists the primary transmission without any active components, leading to low power consumption and no thermal noise added to the reflected signal. IRS also contributes to a squared gain of the number of reflectors on the received signal power, which can be interpreted as a Maximum Ratio Combining (MRC) overlapped to a Maximum Ratio Transmission (MRT).
\end{section}
